\documentclass[11pt]{article}
\usepackage[a4paper,margin=3em]{geometry}
\usepackage[style=ieee,url=false,doi=false,maxbibnames=99,sorting=ydnt,dashed=false]{biblatex}
\bibliography{papers}
% https://en.wikibooks.org/wiki/LaTeX/Colors
\def\theme{OliveGreen}

\usepackage{simplecv}

\begin{document}

\headinginline{Tomasz Nowak}
	{
    Email: \email{tomasz.nowak@tonowak.com} \\
    LinkedIn: \linkedin{tomasz-nowak-tonowak} \\
}{
    GitHub: \github{tonowak} \\
    GitLab: \gitlab{tonowak} \\
}% {PA_zdjecie_twarzy.jpg}

\section{Experience}
\outerlist{
	\entry{\textbf{Jane Street -- Software Developer Internship} \hfill London, 2022 and 2023}
	\innerlist {
		\entry{\textbf{2023, first project:}
				worked with a trader/researcher to implement
				a tool for analyzing and calculating
				some historical data of securities
				for determining risks and benefits of holding a bond.
		}
		\entry{\textbf{2023, second project:}
				made the OCaml language work with gdb/lldb debuggers:
				extended the OCaml compiler with debug
				info of variable types,
				implemented support for variant types
				and for OCaml in lldb.
				Before that, it was not possible to print
				the contents of OCaml variables in the debugger.
				Code is open source \link{https://github.com/ocaml-flambda/flambda-backend/compare/main...tonowak:flambda-backend:dwarf-bool}{here}
				and \link{https://github.com/ocaml-flambda/llvm-project/compare/main...tonowak:llvm-project:add-variant-support}{here}.
		}
		\entry{\textbf{2022, first project:}
				extended a company product for their clients
				to support multiple types of securities.
		}
		\entry{\textbf{2022, second project:}
				designed and implemented an asynchronous system for
				retrieving and sending data across multiple
				sources, with a focus on reconnections,
				error handling and correctness.
		}
	}
}

\section{Education}
\outerlist{
	\entrybig
	{University of Warsaw}{}
	{\textbf{Bachelor's degree} in Computer Science, \textbf{GPA 4.95 / 5.00.}}{2020\textendash 2023}
	\innerlist{
		\entry{One of the \textbf{2 students out of around 160}
			to receive an ,,Exceptional 5!'' final grade.}

		\entry{\link{https://arxiv.org/abs/2308.14623}{My thesis} is about extending a linter for the Rust language
			that detects semantic versioning violations.

			The thesis has made it to the finals of a Polish competition for Computer Science bachelor's theses.

			\textbf{Wrote a \link{https://predr.ag/blog/semver-violations-are-common-better-tooling-is-the-answer/}{blog post}} describing the important results of the thesis.
			Highly upvoted on \link{https://www.reddit.com/r/rust/comments/16cj1mo/semver_violations_are_common_better_tooling_is/}{reddit.com/r/rust}.

			My code in this project is now used by companies like \textbf{Microsoft, Amazon, Mozilla and Adobe},
			and by some of the biggest Rust libraries.}
	}

	\entrybig
	{University of Warsaw}{}
	{\textbf{Master's degree} in Computer Science, work in progress.}{2023\textendash 2025}
	\innerlist{
		\entry{\textbf{Teaching:} I'm conducting classes in \textit{Text algorithms}.
			Got this unique offer while still being a bachelor's student.
		}
	}
}

\section{Competitions (sports programming)}
\denseouterlist{
	\entry{ICPC World Finals: \textbf{finalist of ICPC WF 2022} (which will happen in November 2023).}
	\entry{ICPC Central Europe Regional Contest: \textbf{golden medalist of CERC 2022, medalist of CERC 2021, 2020}.}
	\entry{Central European Olympiad in Informatics: \textbf{winner of CEOI 2020}.}
	\entry{International Olympiad in Informatics: \textbf{medalist of IOI 2020}.}
	\entry{Polish Olympiad in Informatics: \textbf{winner of POI 2020}, medalist of POI 2019, finalist of POI 2018.}
	\entry{Polish Olympiad in Mathematics: finalist of POM 2020 and POM 2019.}
	% \entry{finalist of PA 2020 and PA 2019 (Algorithmic Engagements / Potyczki Algorytmiczne, open competition in Poland) \hfill 2018\textendash 2020}
}

\section{Organization of competitions}
\denseouterlist{
	\entry{\textbf{Vicechair of the Jury} of the Polish Olympiad in Informatics (2023 -- 2025).
		\innerlist{
			\entry{introduced a lot of minor and major changes in the process of preparing the competitions.}
			\entry{initialized the creation of a \link{https://github.com/sio2project/sinol-make}{tool for task preparation}
				and mentored a student during its implementation by giving code review and by helping with decision-making.
				The tool is now widely used in the community.}
			\entry{overseeing the competitions and making the main decisions in case of any unexpected events.}
		}
	}
	\entry{Member of the Jury of the Polish Olympiad in Informatics and Junior Olympiad in Informatics, member of Polish Olympiad in Informatics' Task Commision (2020 -- Current).}
	\entry{Team leader/deputy leader of the Polish national team in IOI 2021, CEOI 2021, BOI 2021, BOI 2022, BOI 2023.}
	\entry{Each year organizing one or two algorithmic camps for high school students to prepare them for competitions.}
}

\sidebyside{
	\section{Languages}
	English, Polish, French
}{
	\section{Programming languages}
	Rust, C++, OCaml, Python, C, Java, Haskell
}

\end{document}
